---
title: "Untitled"
author: "HN"
date: "5/7/2021"
output: html_document
---

Code that processes raw data and outputs the temperature and humidity covariates with the targets data

```{r}

library(tidyverse)
library(ISOweek) 
library(forecast)
library(fable)
library(tsibble)
library(tsibbledata)
library(lubridate)
library(dplyr)
library(neonstore)
```
Download beetle data
```{r message=FALSE}
## Get the latest beetle target data.  
download.file("https://data.ecoforecast.org/targets/beetles/beetles-targets.csv.gz",
              "beetles-targets.csv.gz")
targets <-  read_csv("beetles-targets.csv.gz")
```
Download Humidity data
```{r}
# download all of the weather data
neonstore::neon_download(product="DP4.00001.001")
##Get humidity table
humidity <- neon_read(table = "wss_daily_humid-basic", product = "DP4.00001.001")
```
Summarize humidity data
  note: some weeks don't have humidity data, forcing the min/max fns to produce inf and -inf values, this produces a lot of warning messages when run
```{r}
mean_humidity <- humidity %>%
  mutate(iso_week = ISOweek::date2ISOweek(date)) %>%
  mutate(date = as.Date(date)) %>%
  mutate(time = yearweek(date)) %>%
  group_by(siteID, time) %>%
  summarise(mean_humidity = mean(wssRHMean, na.rm = TRUE), min_humidity = min(wssRHMinimum, na.rm = TRUE), max_humidity = max(wssRHMaximum, na.rm = TRUE))
```
Download Temperature Data
```{r}
#neonstore::neon_download(product = )
# Get temperature data
temp <- neon_read(table = "wss_daily_temp", product = "DP4.00001.001")
```
Summarize Temp Data
  note: this also produces a lot of Infs and -Infs
```{r}
temp_summary <- temp %>%
  mutate(iso_week = ISOweek::date2ISOweek(date)) %>%
  mutate(time = as.Date(date)) %>%
  mutate(time = yearweek(date)) %>%
  group_by(siteID, time) %>%
  summarise(mean_temp = mean(wssTempTripleMean, na.rm = TRUE), min_temp = min(wssTempTripleMinimum, na.rm = TRUE), max_temp = max(wssTempTripleMaximum, na.rm = TRUE))
```
Now add them to targets
```{r}
targets_all <- left_join(targets, mean_humidity, by = c("time", "siteID")) %>% left_join(temp_summary, by = c("time", "siteID"))
```
Clean out the infs, -infs, and NaNs
```{r}
targets_predictors <- targets_all %>%
  mutate("mean_humid" = ifelse(is.nan(mean_humidity), NA, mean_humidity)) %>%
  mutate("min_humid" = ifelse(is.infinite(min_humidity), NA, min_humidity)) %>%
  mutate("max_humid" = ifelse(is.infinite(max_humidity), NA, max_humidity)) %>%
  mutate("mean_tempt" = ifelse(is.nan(mean_temp), NA, mean_temp)) %>%
  mutate("min_tempt" = ifelse(is.infinite(min_temp), NA, min_temp)) %>%
  mutate("max_tempt" = ifelse(is.infinite(max_temp), NA, max_temp)) %>%
  select(-c("min_humidity", "max_humidity", "min_temp", "max_temp", "mean_humidity", "mean_temp"))
```
Write to csv
```{r}
write.csv(targets_predictors, "targets_with_humidity_temperature.csv")
```

