---
title: "cleaned-forecast"
author: "Chloe Cho"
date: "2/17/2021"
output: github_document
---

```{r message=FALSE}
library(tidyverse)
library(ISOweek) 
library(forecast)
library(fable)
library(tsibble)
library(tsibbledata)
library(lubridate)
library(dplyr)
library(neonstore)
library(tibbletime)
library(neon4cast)
```

```{r message=FALSE}
## Get the latest beetle target data.  
download.file("https://data.ecoforecast.org/targets/beetles/beetles-targets.csv.gz",
              "beetles-targets.csv.gz")
targets <-  read_csv("beetles-targets.csv.gz")
```

```{r}
# Get beetles data
beetles <- neon_read(table = "bet_expertTaxonomistIDProcessed-basic", product = "DP1.10022.001")
head(beetles)
```

```{r}
# Get precipitation data
precip <- neon_read(table = "wss_daily_precip-basic", product = "DP4.00001.001")
head(precip)
```

## Including a Predictor (Precipitation)

```{r}
precip_summary <- precip %>%
  mutate(iso_week = ISOweek::date2ISOweek(date)) %>%
  mutate(time = as.Date(date)) %>%
  mutate(time = yearweek(date)) %>%
  group_by(siteID, time) %>%
  summarise(avg_precip = mean(wssPrecipTotal, na.rm = TRUE), min_precip = min(wssPrecipTotal, na.rm = TRUE), max_precip = max(wssPrecipTotal, na.rm = TRUE))
```

Joined beetles and precipitation data. 
```{r}
targets_tsb <- as_tsibble(targets, key = siteID, index = time)

targets_tsb <- targets_tsb %>%
  group_by_key() %>%
  fill_gaps() %>%
  tidyr::fill(abundance, .direction = "down") %>%
  tidyr::fill(richness, .direction = "down") %>%
  filter(time < max(time) - 30)

beetle_precip <- left_join(targets_tsb, precip_summary, by = c("time", "siteID"))
```

```{r}
targets_ts <- beetle_precip %>%
  select(siteID, time, abundance, richness, avg_precip, min_precip, max_precip) %>%
  mutate(iso_week = ISOweek::date2ISOweek(time)) %>%
  separate(iso_week, into = c("year", "week", "day"))  %>%
  mutate(time = ISOweek::ISOweek2date(paste(year,week, "1", sep = "-")))

targets_tsb <- as_tsibble(targets_ts, key = siteID, index = time)
```

```{r}
fit_abundance <- targets_tsb %>%
  model(
    TSLM(abundance ~ avg_precip)
  ) 
fit_abundance

fit_richness <- targets_tsb %>%
  model(
    TSLM(richness ~ avg_precip)
  ) 
fit_richness
```

```{r}
null_fit_abundance <- targets_tsb %>%
  model(NAIVE(abundance)) 
null_fit_abundance

null_fit_richness <- targets_tsb %>%
  model(NAIVE(richness)) 
null_fit_richness
```


```{r}
efi_statistic_format <- function(df){
  ## determine variable name
  var <- attributes(df)$dist
  ## Normal distribution: use distribution mean and variance
  df %>% 
    dplyr::mutate(sd = sqrt( distributional::variance( .data[[var]] ) ) ) %>%
    dplyr::rename(mean = .mean) %>%
    dplyr::select(time, siteID, .model, mean, sd) %>%
    tidyr::pivot_longer(c(mean, sd), names_to = "statistic", values_to = var)
}
```

```{r}
predictors <- targets_tsb %>%
  filter(time > max(time) - 30)
```


Create some forecasts! 

Null forecast (to use to compare scores).
```{r}
null_fc_abundance_score <- forecast(null_fit_abundance, predictors) %>%
  efi_format()
  
null_fc_richness_score <- forecast(null_fit_richness, predictors) %>%
  efi_format()

null_fc_abundance_stats <- forecast(null_fit_abundance, predictors) %>%
  efi_statistic_format()

null_fc_richness_stats <- forecast(null_fit_richness, predictors) %>%
  efi_statistic_format()

null_richness_scores <- neon4cast::score(null_fc_richness_score, "beetles")
null_abundance_scores <- neon4cast::score(null_fc_abundance_score, "beetles")

null_scores <- rbind(null_richness_scores, null_abundance_scores)
```

Forecast with precipitation as a predictor. 
```{r}
fc_abundance_score <- forecast(fit_abundance, predictors) %>%
  efi_format()

fc_richness_score <- forecast(fit_richness, predictors) %>%
  efi_format()

fc_abundance_stats <- forecast(fit_abundance, predictors) %>%
  efi_statistic_format()

fc_richness_stats <- forecast(fit_richness, predictors) %>%
  efi_statistic_format()



forecast <- inner_join(fc_richness_score, fc_abundance_score)
scores <- neon4cast::score(forecast, "beetles")
```

Compare the scores for the null forecast and the regression forecast. 
```{r}
combined_scores <- scores %>%
  inner_join(null_scores, by=c("siteID", "time", "target"))

names(combined_scores)[names(combined_scores) == "score.x"] <- "regression_score"
names(combined_scores)[names(combined_scores) == "score.y"] <- "null_score"
```

```{r}
combined_scores$score_differences = combined_scores$null_score - combined_scores$regression_score
```

Null score is smaller in most cases, or minimally larger than the regression score. Therefore, using precipitation as a predictor for a regression forecast results in a worse forecast than the naive model. 

# Questions

1. Should the final forecast be based on individual sites?
2. What should the format of the actual submission be?
3. How valid is using predictors that only come from some sites?









